Testable normative theories

### 2020-05-03 simple.tex
Tentative def for case gargs for certainty ≠ gargs for possibility
Seems unfructuous because anyway the gargs for certainty must resist rebuttal against possibility, thus mandating that they also be gargs for possibility is free (and much simpler)

\subsection{Definition}
A normative theory is a tuple $(\allprops, ¬, \allargs, I, (\ileadstost[i])_{i \in I}, q, (\gleadsto[q(i)])_{q(i) \in q(I)}, \gbeats, +)$,
with ${\ileadstost[i]} \subseteq (\allargs × \allargs) × \Phi$, ${\gleadsto[q(i)]} \subseteq \allargs × \Phi$, ${\gbeats} \subseteq \allargs × \allargs$,
where $\Phi = \allprops × \set{\text{possible}, \text{sure}}$, and $+$ a commutative associative internal binary operation on $\allargs$. Given $\args \subseteq \allargs$, the notation $\sum \args = \sum_{\ar \in \args} \ar$ thus designates a well-defined argument.

@@

To lighten notations, $\ileadstost[i]$ will generally be denoted by $\ileadstost$, and $\gleadsto[q(i)]$ by $\gleadsto$, with the understanding that these symbols result of applying functions of, respectively, $i$ and $q(i)$. When the symbol $i$, $\ileadstost$ or $\gleadsto$ is used in a formula without $i$ being bound, the binding $\forall i \in I$ is implied.

@@

To ease intuition, let $(\ar', \ar) \ileadstoe \phi$ be equivalent to $(\ar', \ar) \nileadstost ¬\phi$, $\forall \ar', \ar, \phi$.

Given $\phi \in {\gleadsto}(\allargs)$, define ${\ibeatse[!\phi]} \subseteq \allargs × \gargs[\phi]$ such that $\ar' \ibeatse[!\phi] \ar$ iff $(\ar', \ar) \ileadstoe ¬\phi$. Define ${\ibeatse[\phi]} \subseteq \gargs[\phi] × \allargs$ such that $\ar' \ibeatse[\phi] \ar$ iff $(\ar', \ar) \ileadstoe \phi$.

@@

@@

\subsection{Theorem}
\begin{theorem}
	If a theory is answerable, has bounded length, does not repeat, and is operationally valid, it is valid.
\end{theorem}
\begin{proof}
	Lemma: given $\phi \in {\gleadsto}(\allargs)$ and $\ar[k] \in \gargs[\phi]$, if $\ar[k] \nileadstost \phi$, then: $\exists \ar[k + 1] \in \gargs[\phi] \suchthat \card{c(\ar[k + 1])} ≥ \card{c(\ar[k])} + 1$.
	To prove the lemma, let us pick any $\phi \in {\gleadsto}(\allargs)$ and $\ar[k] \in \gargs[\phi]$ such that $\ar[k] \nileadstost \phi$. We know that $\exists \ar_1 \in \allargs \suchthat \ar_1 \ibeatse[!\phi] \ar[k]$. Therefore, by Answerability, $\exists \ar_1' \in \allargs \suchthat \ar_1' \gbeatsstar \ar[k]$, and, by Operational validity, $\exists \ar_2 \in \gargs[\phi] \suchthat \ar_2 \gbeats \ar'_1$. 
	Define $\ar[k + 1] = \ar[k] + \ar_2$. 
	By No repetition, $\ar_2 \notin c(\ar[k])$.
	Thus, $\card{c(\ar[k + 1])} ≥ \card{c(\ar[k])} + 1$.

>>>>

\subsection{Definition}
A normative theory is a tuple $(\allprops, ¬, \allargs, I, (\ileadstoe[i])_{i \in I}, q, (\gleadsto[q(i)])_{q(i) \in q(I)}, \gbeats, +)$,
with ${\ileadstoe[i]} \subseteq (\allargs × \allargs) × \Phi$, ${\gleadsto[q(i)]} \subseteq \allargs × \Phi$, ${\gbeats} \subseteq \allargs × \allargs$,
where $\Phi = \allprops × \set{\text{possible}, \text{sure}}$, and $+$ a commutative associative internal binary operation on $\allargs$. Given $\args \subseteq \allargs$, the notation $\sum \args = \sum_{\ar \in \args} \ar$ thus designates a well-defined argument.

@@

Given any $\ar', \ar, \prop$, let $(\ar', \ar) \ileadstost (\prop, \text{sure})$ be equivalent to $(\ar', \ar) \nileadstoe (¬\prop, \text{poss}) \land (\ar', \ar) \ileadstoe (\prop, \text{sure}) \land (\ar', \ar) \nileadstoe (¬\prop, \text{sure})$; and $(\ar', \ar) \ileadstost (\prop, \text{poss})$ be equivalent to $(\ar', \ar) \nileadstoe (¬\prop, \text{sure})$.
\footnote{Assume $i$, given $\ar$ and $\ar'$, picks repeatedly (in various circumstances) nonempty subsets of $\set{\prop, ¬\prop}$. Define $(\ar', \ar) \ileadstoe (\prop, \text{sure})$ iff she sometimes chooses $\set{\prop}$ and $(\ar', \ar) \ileadstoe (\prop, \text{poss})$ iff she sometimes chooses $\set{\prop}$ or $\set{\prop, ¬\prop}$. Then, $(\ar', \ar) \ileadstost (\prop, \text{sure})$ iff she always chooses $\set{\prop}$ and $(\ar', \ar) \ileadstost (\prop, \text{poss})$ iff she always chooses either $\set{\prop}$ or $\set{\prop, ¬\prop}$.}

To lighten notations, $\ileadstoe[i]$ will generally be denoted by $\ileadstoe$, and $\gleadsto[q(i)]$ by $\gleadsto$, with the understanding that these symbols result of applying functions of, respectively, $i$ and $q(i)$. When the symbol $i$, $\ileadstost$ or $\gleadsto$ is used in a formula without $i$ being bound, the binding $\forall i \in I$ is implied.

@@

@@

Given $\phi \in {\gleadsto}(\allargs)$, define ${\ibeatse[!\phi]} \subseteq \allargs × \gargs[\phi]$ such that, when $\phi = (\prop, \text{sure})$, $\ar' \ibeatse[!\phi] \ar$ iff $(\ar', \ar) \ileadstoe (¬\prop, \text{poss}) \lor (\ar', \ar) \ileadstoe (¬\prop, \text{sure})$, and when $\phi = (\prop, \text{poss})$, $\ar' \ibeatse[!\phi] \ar$ iff $(\ar', \ar) \ileadstoe ¬\phi$. Define ${\ibeatse[\phi]} \subseteq \gargs[\phi] × \allargs$ such that $\ar' \ibeatse[\phi] \ar$ iff $(\ar', \ar) \ileadstoe \phi$.

@@

\begin{definition}[Claiming certainty requires claiming possibility]
	$\forall (\prop, \text{sure}) \in {\gleadsto}(\allargs): (\prop, \text{poss}) \in {\gleadsto}(\allargs)$.
\end{definition}

\begin{definition}[Challenging possibility implies challenging certainty]
	$\forall (\prop, \text{sure}) \in {\gleadsto}(\allargs), \ar_1 \in \allargs, \ar_0 \in \gargs[(\prop, \text{sure})]: (\ar_1, \ar_0) \ileadstoe (¬\prop, \text{sure}) ⇒ (\ar_1, \ar_0) \ileadstoe (¬\prop, \text{poss})$.
\end{definition}

\subsection{Theorem}
\begin{theorem}
	If a theory is answerable, has bounded length, does not repeat, and is operationally valid, it is valid.
\end{theorem}
\begin{proof}
	Lemma: given $\phi \in {\gleadsto}(\allargs)$ and $\ar[k] \in \gargs[\phi]$, if $\ar[k] \nileadstost \phi$, then: $\exists \ar[k + 1] \in \gargs[\phi] \suchthat \card{c(\ar[k + 1])} ≥ \card{c(\ar[k])} + 1$.
	To prove the lemma, let us pick any $\phi \in {\gleadsto}(\allargs)$ and $\ar[k] \in \gargs[\phi]$ such that $\ar[k] \nileadstost \phi$. 
	We know that $\exists \ar_1 \in \allargs \suchthat (\ar_1, \ar[k]) \nileadstost \phi$.

	We want to prove, first, that $(\ar_1, \ar[k]) \ileadstoe ¬\phi$. If $\phi = (\prop, \text{poss})$, that is clear from the definition of $\ileadstost$. If $\phi = (\prop, \text{sure})$,

	\commentOC{With new definition of $\ileadstost$, when $\phi = (\prop, \text{sure})$, from $\ar \nileadstost \phi$ we only obtain that $\ar \ileadstoe ¬\phi \lor …$, thus, we still need to show that $\ileadstoe (\prop, \text{sure})$ and that $\nileadstoe (¬\prop, \text{sure})$.}
	We know that $\exists \ar_1 \in \allargs \suchthat \ar_1 \ibeatse[!\phi] \ar[k]$. Therefore, by Answerability, $\exists \ar_1' \in \allargs \suchthat \ar_1' \gbeatsstar \ar[k]$, and, by Operational validity, $\exists \ar_2 \in \gargs[\phi] \suchthat \ar_2 \gbeats \ar'_1$. 
	Define $\ar[k + 1] = \ar[k] + \ar_2$. 
	By No repetition, $\ar_2 \notin c(\ar[k])$.
	Thus, $\card{c(\ar[k + 1])} ≥ \card{c(\ar[k])} + 1$.
